\documentclass{report}
\usepackage[a4paper, total={6in, 10in}]{geometry}
\title{Ethics}
\date{}
\author{andi bandi shandi, jo iss subject mein fail hua uski \dots}
\begin{document}
\maketitle
\section*{Ethics}
Ethics refers to the moral principles and values that guides the human behaviour and decision making. It is a branch of philosophy that deals with questions about what is right or wrong, good, or bad. How individuals should conduct themselves in various situations.
\section*{Some key aspects of Ethics}
\subsection*{Morality}
Ethics is considered with moral principles and the concept of right and wrong. It explores the question related to what is considered ethical behaviour.
\subsection*{Consequences}
Ethical discussions often consider potential consequences of actions on individuals, society, or the environment. Ethical reasoning aims to minimize harm and maximize benefit.
\subsection*{Integrity}
Commonly termed together with honesty and trustworthiness. It involves acting consistently with one's belief and principles even in the face of challenges.
\subsection*{Fairness}
Ethical actions prioritize fairness of equity. treating all individuals with respect and without discrimination. Fairness involves considering the interests of all.
\subsection*{Accountability}
Ethical decision making involves taking responsibility for one's actions and being accountable for the consequences of those actions.
\subsection*{Societal Norms}
Ethical standards are influenced by societal norms, cultural values, and legal frameworks. What is considered ethical can vary across diverse cultures and societies.
\section*{Legal Issues}
\subsection*{Copyright Infringement}
It occurs when someone uses, reproduces, distributes, or displays copyrighted material without the permission of the owner. The copyright protects original works of authorship such as books, music, films, software, and artwork. Infringing on copyright can lead to legal consequences.
\subsection*{Patent Infringement}
Patent infringement involves the unauthorized manufacturing, selling, or using of a patented invention or technology.

A patent grants the inventor exclusive rights to their invention for a limited period, 20 years. If someone else produces, sells, or uses the patented invention without permission, they may be liable for patent infringement.
\subsection*{Trademark Infringement}
It occurs when someone uses a registered trademark or a confusingly similar mark without authorization, causing consumer confusion about the source of the goods or services. Trademarks protect brand names, logos and symbols that distinguish products or services in the marketplace. Unauthorized use of a trademark can lead to legal action and potential damages.
\subsection*{Trade Secret Misappropriation}
It involves the unauthorized acquisition or disclosure of confidential business information that supply a competitive advantage. Trade secrets can include formulas, processes, customer list or other valuable proprietary information. Businesses must take measures to protect their trade secrets, and if someone improperly gets or shares this information, it can result in legal action and significant harm to the affected company.
\section*{Importance of integrity}
\subsection*{Trustworthiness}
Integrity builds trust with others when you consistently act with honesty and ethics, people trust you and feel confident in your words and actions.
\subsection*{Positive Reputation}
Demonstrating integrity leads to a positive reputation. It earns you respect and admiration from colleagues, friend, and the broader community.
\subsection*{Ethical Decision Making}
Integrity guides ethical decision making. It helps us make choices based in principles and values even in challenging situations.
\subsection*{Long Term Success}
Individuals and organizations with integrity try to achieve long term success as they prioritize ethics over short term gains.
\subsection*{Consistency}
Integrity means being consistent in your behaviour and actions. This consistency fosters stability and reliability in relationships and work.
\section*{Ethics in Business World}
Ethics in business world refers to the applications of moral principles and values in all aspects of business operations and decision making. It involves conducting business in an honest, fair, and responsible manner. Considering the impact of actions on stakeholders, the environment and society.
\section*{Some key aspects of ethics in business world}
\subsection*{Integrity and Honesty}
Upholding integrity and honesty in all business dealings, interactions, and communications.
\end{document}